Combined effects of protein expression variance and correlation on multicomponent systems

### 2020-03-11 Manuscript/Manuscript.Rmd
.

```{r figure_1, echo=FALSE, fig.height=4, fig.width=6, message=FALSE, warning=FALSE, fig.cap=fig_legend_1}
allGroups <- readRDS("allGroups.RDS")

@@

top / bottom + plot_layout(nrow = 2) +
  plot_annotation(tag_levels = "A")

@@

```{r figure_2, echo=FALSE, fig.height=7, fig.width=6, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_2}
p1 <- ggplot(allGroups, aes(x = normVar, fill = interval)) + 
  geom_histogram(bins = 50) + theme_minimal() +
  #scale_fill_viridis_d()
  scale_fill_manual(values = c("#d53e4f","#3288bd","grey")) +
  xlab("Normalized Variation") + ylab("Number")

@@

p2 <- ggplot(filter(allGroups, n > 5), aes(x = medCors, y = medCV, color = interval)) +
  geom_point(data = filter(allGroups, interval == "mid", n > 4),
             size = 2, alpha = 0.5, stroke = 0) +
  geom_point(data = filter(allGroups, interval != "mid", n > 4),
             size = 3, alpha = 0.75, stroke = 0) +
  geom_label_repel(data = filter(allGroups, accession %in% interesting_groups),
                  aes(label = name),
                  colour = 'black',
                  size = 1.5,
                  force = 5,
                  box.padding = 1) +
  #coord_cartesian(ylim=c(-10,10)) +
  theme_minimal() +
  theme(legend.position = "none") +
  scale_color_manual(values = c("#d53e4f","#3288bd","grey")) +
  xlab("Mean Correlation") + ylab("Mean Coefficient of Variation")

p3 <- ggplot(allGroups, aes(x = medCors, fill = interval)) +
  annotate("rect", xmin = 0.15, xmax = Inf, ymin = 0, ymax = Inf, fill = "orange", alpha = 0.5) +
  geom_density(data = filter(allGroups, interval != "mid"), alpha = 0.75, color = NA) +
  geom_density(data = filter(allGroups, interval == "mid"), alpha = 0.5, color = NA) +
  theme_minimal() +
  scale_fill_manual(values = c("#d53e4f","#3288bd","grey"))

p4 <- ggplot(allGroups, aes(x = medCV, fill = interval)) +
  geom_density(alpha = 0.75, color = NA) +
  theme_minimal() +
  scale_fill_manual(values = c("#d53e4f","#3288bd","grey"))

@@

p6 <- p2 + plot_spacer() + plot_layout(widths = c(1,0.5))

(p1 + p3 + p4) / p6 + plot_layout(heights = c(1,5)) +
  plot_annotation(tag_levels = "A") &
  theme(legend.position = "none")

>>>>

```{r figure_1, echo=FALSE, fig.height=4.5, fig.width=6, message=FALSE, warning=FALSE, fig.cap=fig_legend_1}
allGroups <- readRDS("allGroups.RDS")

@@

top / bottom + plot_layout(nrow = 2,
                           heights = c(1,0.8)) +
  plot_annotation(tag_levels = "A")

@@

```{r figure_2, echo=FALSE, fig.height=7, fig.width=6, message=FALSE, warning=FALSE, eval=TRUE, fig.cap=fig_legend_2}
p1 <- ggplot(allGroups, aes(x = normVar, fill = interval)) + 
  geom_histogram(bins = 50) + theme_minimal() +
  #scale_fill_viridis_d()
  scale_fill_manual(values = c("#d53e4f","#3288bd","grey")) +
  xlab("Normalized Variation") + ylab("Number") +
  theme(legend.position = "none")

@@

p2 <- ggplot(filter(allGroups, n > 5), aes(x = medCors, y = medCV, color = interval)) +
  geom_point(data = filter(allGroups, interval == "mid", n > 4),
             size = 2, alpha = 0.5, stroke = 0) +
  geom_point(data = filter(allGroups, interval != "mid", n > 4),
             size = 3, alpha = 0.75, stroke = 0) +
  geom_label_repel(data = filter(allGroups, accession %in% interesting_groups),
                  aes(label = name),
                  colour = 'black',
                  size = 1.5,
                  force = 5,
                  box.padding = 1) +
  #coord_cartesian(ylim=c(-10,10)) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("#d53e4f","#3288bd","grey")) +
  xlab("Mean Correlation") + ylab("Mean Coefficient of Variation")

p3 <- ggplot(allGroups, aes(x = medCors, fill = interval)) +
  annotate("rect", xmin = 0.15, xmax = Inf, ymin = 0, ymax = Inf, fill = "orange", alpha = 0.5) +
  geom_density(data = filter(allGroups, interval != "mid"), alpha = 0.75, color = NA) +
  geom_density(data = filter(allGroups, interval == "mid"), alpha = 0.5, color = NA) +
  theme_minimal() +
  scale_fill_manual(values = c("#d53e4f","#3288bd","grey")) +
  theme(legend.position = "none")

p4 <- ggplot(allGroups, aes(x = medCV, fill = interval)) +
  geom_density(alpha = 0.75, color = NA) +
  theme_minimal() +
  scale_fill_manual(values = c("#d53e4f","#3288bd","grey")) +
  theme(legend.position = "none")

@@

# p6 <- p2 + plot_spacer() + plot_layout(widths = c(1,0.5))
#   
# (p1 + p3 + p4) / p6 + plot_layout(heights = c(1,5)) +
#   plot_annotation(tag_levels = "A") &
#   theme(legend.position = "none")

left <- (p1 / p3 / p4) + plot_layout(ncol = 1)

wrap_plots(left, p2) + plot_layout(widths = c(1,3)) +
  plot_annotation(tag_levels = "A")
